Measurement of total hadronic differential cross sections in the LArIAT experiment

### 2018-04-29 Chapter-2/2-LArTPCs.tex
s

\begin{figure}[hbpt]
\centering
\includegraphics[width=0.45\textwidth]{Chapter-2/Images/NueCCSim.png}	
\includegraphics[width=0.45\textwidth]{Chapter-2/Images/MomentumKaonsDatabeamline.png}
\caption{$Left$. Simulation of the products of a $\nu_e$ CC interaction in DUNE, both in particles type and momentum. \\
$Right$. Momentum spectrum for low mass particles ($e,\mu,\pi$) in the LArIAT beamline,  negative tune. Data is shown in black, while the beamline simulation is shown in solid colors. }
\label{fig:NuSimulation}
\end{figure}

\begin{figure}[hbpt]
\centering
\includegraphics[width=0.45\textwidth]{Chapter-2/Images/pdkGenie.png}	
\includegraphics[width=0.45\textwidth]{Chapter-2/Images/MomentumKaonsDatabeamline.png}
\caption{$Left$. Momentum of the kaon outgoing a proton decay $p\rightarrow K^+\bar\nu$ event as simulated by the Genie 2.8.10 event generator in argon. The red line represents the kaon momentum distribution before undergoing the simulated final state interaction inside the argon nucleus, while the blue line represents the momentum distribution after FSI.\\
$Right$. Positive Kaon momentum spectrum in the LArIAT beamline. }
\label{fig:PDKGENIE}
\end{figure}

>>>>

\begin{figure}[hbpt]
\centering
\includegraphics[width=0.45\textwidth]{Chapter-2/Images/NueCCSim.png}	
\includegraphics[width=0.45\textwidth]{Chapter-2/Images/MomentumKaonsDatabeamline.png}
\caption{$Left$. Simulation of the products of a $\nu_e$ CC interaction in DUNE, both in particles type and momentum. \\
$Right$. Momentum spectrum for low mass particles ($e,\mu,\pi$) in the LArIAT beamline,  negative tune, Run II, High Yield see section \ref{sec:MWPCfunc}. }
\label{fig:NuSimulation}
\end{figure}

\begin{figure}[hbpt]
\centering
\includegraphics[width=0.45\textwidth]{Chapter-2/Images/pdkGenie.png}	
\includegraphics[width=0.45\textwidth]{Chapter-2/Images/MomentumKaonsDatabeamline.png}
\caption{$Left$. Momentum of the kaon outgoing a proton decay $p\rightarrow K^+\bar\nu$ event as simulated by the Genie 2.8.10 event generator in argon. The red line represents the kaon momentum distribution before undergoing the simulated final state interaction inside the argon nucleus, while the blue line represents the momentum distribution after FSI.\\
$Right$. Positive Kaon momentum spectrum in the LArIAT beamline,  positive tune, Run II, Picky Tracks see section \ref{sec:MWPCfunc}. }
\label{fig:PDKGENIE}
\end{figure}
